% !TEX root = mythesis.tex

\chapter{Conclusion}

The purpose of this thesis was to discuss how to solve polynomial optimization problems. We did this by first discussing optimization problems in general, and focused on the case of semidefinite programming. From there, we discussed how we can find the optimal value for any polynomial by rewriting it with a nonnegativity constraint, which we then rewrote as a sos constraint. This allowed us to apply our semidefinite programming to our polynomial optimization problems, which meant that we could quickly solve them.

As much as we have covered in this thesis, there are still several areas we would like to explore that are related to what we covered here.

\begin{enumerate}
	\item \textbf{ADMM and Interior Point Methods} - While we briefly discussed the methods that our solvers utilized in order to solve semidefinite programming problems, we did not get to truly dig into the details and determine why our numerical experiments obtained the results they did. It would be interesting to explore these methods and see if they could be improved upon. 
	
	\item \textbf{Other Applications} - Needless to say, there is more than one application of polynomial optimization. In \cite{Ahmadi2016a} alone, there is also applications involving Lyapunov theory, as well as nonlinear control design for quadrotors. These applications would be fascinating to explore. 
	
	\item \textbf{The Wireless Transmitter Placement Problem} - While our application was interested in determining transmission rates for transmitters with given placements, it did not explore the possibility of placing transmitters in the optimal locations. It would be interesting to explore how this changed the problem formulation. 
\end{enumerate}